Rhythmic Density for Sonifying Quantum Superpositions

### 2023-07-20 isqcmc2023_latex/paper_isqcmc.tex
small revisions

We would like to thank Eduardo Miranda Reck for pioneering the field of quantum computer music, and for inviting us to submit a paper to ISQCMC. We would also like to thank Adrian German for creating a space for quantum computing at Indiana University Bloomington, and for his help and support in learning this field.

>>>>

We would like to thank Eduardo Reck Miranda for pioneering the field of quantum computer music, and for inviting us to submit a paper to ISQCMC. We would also like to thank Adrian German for creating a space for quantum computing at Indiana University Bloomington, and for his help and support in learning this field. Thanks to John Gibson and Chi Wang at the Center for Electronic and Computer Music for their support as well!
